### 2017-03-01 ResearchNotes/books.tex
Adds papers and books descriptions to notes

Book is~\cite{book_dm_practical}.~\TODO{}

>>>>

This Book~\cite{book_dm_practical} is very practical not only because it talk
about many models, but also because is talk about how Machine Learning and data
Mining relate. Such notion might be important in the thesis text or, at the
very least, it might be important is someone asks why I cite sources about
Machine Learning.

The usual classifier models, such as decision trees, and usual clustering
methods are specified in this book.

### 2017-03-01 ResearchNotes/papers.tex
Adds papers and books descriptions to notes

\section{Initial Papers in Detail}

@@

>>>>

\section{Papers}

@@

% =============================================================================
\subsection{\texttt{IND\_010} - E-learning: emerging uses, empirical results
and future directions}

Paper is~\cite{ind_010}.

What is taken from this paper is how e-learning has been growing in popularity
as a way to deliver training online. Organizations such as Universities have
been using E-Learning recently due to advances in technology and the increasing
use of the Internet.

One other point taken from this paper is how E-Learning platforms are used to
track users in terms of their usage of the platforms, their habits, etc.
Studying this data can be useful to the organizations that make use of
E-Learning.

% =============================================================================
\subsection{\texttt{IND\_011} - A Learning Management System Including
Laboratory Experiments on Measurement Instrumentation}

Paper is~\cite{ind_011}.

This paper supports the notion that~\gls{lms} systems are platforms for content
distribution, and that the content they distribute have authors and learners.
These two roles are basically the Professors and Students, respectively, in
Moodle.

Like in Moodle, the authors will create and publish content that is relevant
for a training/learning process in the scope of college courses or any other
E-Learning scenario. The learners will consume that content when performing
their training or when studying courses.

% =============================================================================
\subsection{\texttt{IND\_012} - M-Learning - a New Stage Of E-Learning}

Paper is~\cite{ind_012}.

This paper introduces the notion of M-Learning, with the M standing for mobile.
M-Learning is like E-Learning but aims at delivering content and training to
mobile devices which are connected to the Internet.

M-Learning is presented as a subset of E-Learning, that is, a more limited
notion of E-Learning, since platforms for it would be developed aiming for
tablet PCs, mobile phones, and other such devices. Content would also be
produced, organized, and published in such a way as to fit the devices in
question and the usage of those devices.

This paper doesn't really have anything relevant for this project, and it also
doesn't cite any relevant sources for it.

% =============================================================================
\subsection{\texttt{IND\_013} - Can E-Learning Replace Classroom Learning?}

Paper is~\cite{ind_013}.

A comparison between traditional classroom learning and E-Learning is made in
this paper. The most relevant thing for this project is the fact that the paper
supports the notion that E-Learning as been on the rise for life-long learning,
on-the-job learning, and distance learning.

% =============================================================================
\subsection{\texttt{IND\_014} - Moodle: Using learning communities to create an
open source course management system}

Paper is~\cite{ind_014}.

The paper describes PhD research about data generated in a Moodle instance in
the first few experiments made when the platform was starting out to be
developed and used.

The main question the paper looks into the answering is following question:

``How can internet software successfully support social constructionist
epistemologies of teaching and learning?''

It doesn't go into much detail regarding the actual data that Moodle stores,
but it talks about the design of Moodle, which is a~\gls{lms}, even if it
doesn't use that term.

The kind of data that the study looks into is relevant in terms of building a
successful~\gls{lms}, but none of it is relevant in terms of~\gls{edm}.
\gls{edm} is about the mining of data generated by a~\gls{lms} in order to find
patterns in training methods. This study is about looking into the usage of the
actual platform itself.
